% By Savir Singh
% Savir's Current Resume

\documentclass[10pt,a4paper,sans]{moderncv} 
\usepackage[super]{nth}


% moderncv themes
\moderncvstyle{banking} % classic, banking, casual, oldstyle, fancy
\moderncvcolor{blue}

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Savir}{Singh}
\address{Oakville, ON}{Canada}
\email{savirsinghwork@gmail.com}
\homepage {savirsingh.github.io}
\social[github]{savirsingh}

\begin{document}
\hypersetup{pdftitle={Savir's Résumé}} % <====================================

\makecvtitle

\section{Summary}
\cvitem{}{Innovative web and software developer with 3+ years of experience in building full-stack applications. Experienced in competitive programming, having written and won some algorithmic contests as well.}

\section{Skills}
\cvitem{Programming}{Python, C/C++, Java, SQL}
\cvitem{Web Development}{React, HTML, CSS, JavaScript}
\cvitem{Other}{Git, Windows}

\section{Work Experience}
\cventry{2023--Present}{Volunteer Programming Tutor}{My Code Club}{Mississauga, ON}{}{
\begin{itemize}
\item Helped to teach youth aged 4-13 how to build apps.
\item Used App Inventor to build mobile apps.
\end{itemize}
}

\section{Achievements}
\cventry{2023}{Halton District School Board}{Halton Skills Coding Competition - Gold Medalist}{Burlington, ON}{}{One of two high school students that represented Garth Webb in the competition. Only student from grade 10 selected. The next step is competing in the Skills Ontario Competition in Toronto during May 2023.}
\cventry{2021, 2022}{PEO-Mississauga Chapter}{High School Coding Contest - \nth{1} Place in 2021 and 2022}{Mississauga, ON}{}{}
\cventry{2021}{My Code Club}{Code-A-Thon 2021 - \nth{1} Place}{Mississauga, ON}{}{}
\cventry{2020}{PEO-Mississauga Chapter}{Mathletics 2020 - \nth{1} Place}{Mississauga, ON}{}{}
\cventry{2019}{The Rockhampton Grammar School}{Japanese Award - Top Mark in Grade}{Rockhampton, Australia}{}{Achieved a mark of 100\% in Japanese.}

\section{Activities \& Extracurriculars}
Tennis (won regional competition in Australia), Swimming, Chess (plays casually), Competitive Programming (won several contests)

\section{Education}
\cventry{2021--2025}{Ontario Secondary School Diploma}{Garth Webb Secondary School}{Oakville, ON}{}{} {
\begin{itemize}
    \item Listed on Honour Roll for high-achieving students in Grade 9.
\end{itemize}
}

\end{document}
